Timbral similarity between extended playing techniques: the next frontier in querying instrumental databases

### 2018-01-29 paper/lagrangeSpontaneousSimilarity2017.tex
capitalization of "next section"

As it will be discussed in the next Section, the main application scenario that is considered in this paper is the recommendation of sounds based on exemplar. This involves the definition of a similarity measure that behave similarly to the human perception. In this paper, the reference used for assessing similarity to human perception is the perceptual data gathered in experiment 2.

@@

We investigated the capabilities of the proposed system to model a perceptual space averaged over several subjects. For application purposes that will be discussed in the next Section, it can be useful to consider the reference clustering of only one user and see if the system perform well with this kind of reference. To do so, the evaluation protocol is slightly modified. First the secondary stage is optimized for the 31 reference clusterings independently and for each resulting projection the precision is computed. The 31 precision measures are then averaged and shown in Table \ref{tab:res2}. The excellent results of the TST optimized using LMNN demonstrates the usefulness of the proposed approach to model complex similarity space such as the perceptual ones gathered in Experiment 2.

>>>>

As it will be discussed in the next section, the main application scenario that is considered in this paper is the recommendation of sounds based on exemplar. This involves the definition of a similarity measure that behave similarly to the human perception. In this paper, the reference used for assessing similarity to human perception is the perceptual data gathered in experiment 2.

@@

We investigated the capabilities of the proposed system to model a perceptual space averaged over several subjects. For application purposes that will be discussed in the next section, it can be useful to consider the reference clustering of only one user and see if the system perform well with this kind of reference. To do so, the evaluation protocol is slightly modified. First the secondary stage is optimized for the 31 reference clusterings independently and for each resulting projection the precision is computed. The 31 precision measures are then averaged and shown in Table \ref{tab:res2}. The excellent results of the TST optimized using LMNN demonstrates the usefulness of the proposed approach to model complex similarity space such as the perceptual ones gathered in Experiment 2.
